Title: "R lab 2"
author: "Sailesh Arya"
output : html_notebook 


# variables 
Task 1 Crete a variable x and y. store the product of both variable int z 
```{r}
x = 2+5 ; 
y = 6;
z = x*y ; 
z
```
Task 2 Create a new variable but with different method but same result.
```{r}
a <- 10 - 7 
b<- 4 
c<-a/b 
c 
```
# Functions 
Task 3 Create a vector(one dimensional array)
```{r}
 x = c(100,200,300)
 x 
```

# Data Types in R 

Task 4 Create a varable x and check the class and data types of X 
```{r}
 x = 5
 class(x)
 
 
```
```{r}
 is.integer(x)
```

# Vector,matrices , Array, List and Data Frames 
Task 4 Create a matrix "xx" that have 3 row and 2 column and check the class,lenght,dim of the matrix 
```{r}
xx = matrix(1:6, nrow =3, ncol = 2)
xx

class(xx)       # print xx
is.vector(xx)      # check if it is vector or not 
length(xx)        # TO CHECK THE LENGTH 
is.matrix(xx)     # TO CHECK IF it is a matrix or not 
dim(xx)           # to check the dimension of the matrix 


```
# Data Set to apply family tutorial 
Task 5: Import a data with the name of mtcars Table  and given 
import the 6 data type from it 
```{r}
data("mtcars")    #to import table Data  
head(mtcars)    # to see the first 5 value

```
Task 6 : Applied a transpose in build in data set beaver1 and Show the max value in row wise only.
```{r}
apply(t(beaver1),1,max)
```
Task 7: Use a apply function to show the mean value of the given data set.

```{r}
  apply(mtcars,2,mean)

```
Task 8: Create a anonymous function which gives the remainder of 10

```{r}
head(apply(mtcars,2,function(x) x%%10))
```
# lapply Functions 
Task 10: Create a variable called movie and applied a applyl function to conver the data into lowe case and print the movie_Lower in strucutre way
```{r}
movies <- c("SPYDERMAN","BATMAN","VERTIGO","CHINATOWN")
movies_lower <-lapply(movies,tolower)
str(movies_lower)
```
Task 11: Remove a list and unlist it using sapply function 

```{r}
movies_lower <-unlist(lapply(movies, tolower))
str (movies_lower)
```
#sapply()Function
Task 12 :  

```{r}
 dt <- cars
lmn_cars <- lapply(dt, min )
smn_cars <- sapply(dt, min)
lmn_cars
smn_cars

```
```{r}
lmxcars <- lapply(dt, max)
smxcars <- sapply(dt,max)
lmxcars
```

# SAVING AND LOADING DATA 
Task 13 : Create a two variable named with EUCountryNames and EUPopulaltion, and set it as a new data and print it 

```{r}
EUCountyNames = c("United Kingdom", "Germany","france","Italy")
EUPopulations = c(34663466346,363463636,34363664663,6634634634)
EU = data.frame(EUCountyNames,EUPopulations)
EU
```

```{r}
 save(EU,file = "EUinfo.RData")
getwd()
```
```{r}
rm(EU)
load("EUinfo.RData")
write.csv(EU,"EUInfo.csv")


```

```{r}
EU2 = read.csv("EUinfo.v2")
```

